Supplementary Files

### 2018-01-19 Source/Supplementary_Files/supplementary_files.Rmd
Update paper figures and supplementary materials
Complete Supplementary Table S8 in script format

## Negative Genetic interactions 
```{r}

@@

## Protein interaction networks
```{r}

@@

## Kinase-substrate network
```{r}

@@

## Transcriptional regulatory network
```{r}

@@

## Build phenotype master table 
```{r}

@@

## Paralogs and Ohnologs
```{r}

@@

## All interactions combined together  (part 1)
```{r}

@@

## Get densely annotated triplets 
```{r}

@@

## Interactions that are part of triplets, excluding those that are not part of triplets
```{r}

@@

## All interactions combined together  (part 2)
```{r}

@@

>>>>

## Supplementary Table S1. Negative Genetic interactions 
```{r}

@@

## Supplementary Table S2. Protein interaction networks
```{r}

@@

## Supplementary Table S3. Kinase-substrate network
```{r}

@@

## Supplementary Table S4. Transcriptional regulatory network
```{r}

@@

## Helper Codes: Build phenotype master table 
```{r}

@@

## Supplementary Table S6. Paralogs and Ohnologs
```{r}

@@

## Helper Codes: All interactions combined together  (part 1)
```{r}

@@

## Table S9. The list of all the triplets in the filtered integrated network and triplets with genes that are cell cycle-regulated, essential and toxic on overexpression, and their shared phenotype on knockout and GO slim terms.
```{r}

@@

## Helper Codes: Interactions that are part of triplets, excluding those that are not part of triplets
```{r}

@@

## Supplementary Table S7: All interactions combined together  (part 2)
```{r}

@@

## Supplementary Table S8. The number of interactions in the integrated biological network. (Part 1)
```{r}

## Full Integrated Newtork

# Genetic interactions

all_negative_gi_helper_a <- filtered_costanzo_stringent[ , c("query_oln_id_edited", "array_oln_id_edited") ] %>%
							dplyr::rename( oln_id_a=query_oln_id_edited) %>%
							dplyr::rename( oln_id_b=array_oln_id_edited)

all_negative_gi_helper_b <- filtered_costanzo_stringent[ , c("query_oln_id_edited", "array_oln_id_edited") ] %>%
							dplyr::rename( oln_id_b=query_oln_id_edited) %>%
							dplyr::rename( oln_id_a=array_oln_id_edited)

all_negative_gi <- dplyr::union  (all_negative_gi_helper_a, all_negative_gi_helper_b ) %>%
					dplyr::distinct() %>%
				   dplyr::filter( oln_id_a >= oln_id_b )

# Number of interactions
all_negative_gi_counts <- dplyr::count( all_negative_gi)[[1]]
all_negative_gi_counts

# Number of proteins
 c( all_negative_gi [, "oln_id_a"], all_negative_gi [, "oln_id_b"] ) %>% unique() %>% length()

# Kinase-substrate network

 # Number of interactions
 kinase_network_filtered %>%
     dplyr::select (one_of(c("kinase_oln_id", "target_oln_id"))) %>%
     dplyr::distinct()%>%
     dplyr::count()

 # Number of proteins
 c( kinase_network_filtered [, "kinase_oln_id"], kinase_network_filtered [, "target_oln_id"] ) %>% unique() %>% length()

 # Number of kinases 
 kinase_network_filtered [, "kinase_oln_id"]  %>% unique() %>% length()

 # Protein interaction network
  # Number of interactions
 sbi_interactome %>%
     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
     dplyr::filter( oln_id_a > oln_id_b) %>%
     dplyr::distinct()%>%
     dplyr::count()

  # Number of proteins
 c( sbi_interactome [, "oln_id_a"], sbi_interactome [, "oln_id_b"] ) %>% unique() %>% length()

# Transcriptional regulatory network

# Number of interactions
 tf_network_collated %>%
    dplyr::filter( interaction_type_abbrev == 'td' ) %>%
     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
     dplyr::distinct()%>%
     dplyr::count()

# Number of proteins
 c( tf_network_collated [, "oln_id_a"][[1]], tf_network_collated [, "oln_id_b"][[1]] ) %>% unique() %>% length()

# Number of transcription factors
 tf_network_collated %>%
    dplyr::filter( interaction_type_abbrev == 'td' ) %>%
     dplyr::select (one_of(c("oln_id_a"))) %>%
     dplyr::distinct()%>%
     dplyr::count()

# Total Number of Interactions (Unique Pairs of Proteins)
interactions_combined %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
  dplyr::filter (oln_id_a > oln_id_b) %>%
  dplyr::distinct()%>%
  dplyr::count()

# Total Number of Proteins 
 c( interactions_combined [, "oln_id_a"], interactions_combined [, "oln_id_b"] ) %>% unique() %>% length()

# Total Number of Interactions (Non-unique pairs and direction)
interactions_combined %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
  dplyr::filter (oln_id_a > oln_id_b) %>%
  dplyr::count()

## Supplementary Table S8. The number of interactions in the integrated biological network. (Part 2)
```{r}

### Filtered Newtork: triplets with a single negative genetic interaction

interactions_from_triplet_motifs_simp <- interactions_from_triplet_motifs %>%
                                         dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev")))

 ###################
# Genetic interactions

triplets_negative_gi_helper_a <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "ng" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))

triplets_negative_gi_helper_b <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "ng" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
              							dplyr::rename( temp=oln_id_a) %>%
              							dplyr::rename( oln_id_a=oln_id_b) %>%
                            dplyr::rename( oln_id_b=temp)

triplets_negative_gi <- dplyr::union  (triplets_negative_gi_helper_a, triplets_negative_gi_helper_b ) %>%
					dplyr::distinct() %>%
				   dplyr::filter( oln_id_a >= oln_id_b )

# Number of interactions
triplets_negative_gi_counts <- dplyr::count( triplets_negative_gi)[[1]]
triplets_negative_gi_counts

# Number of proteins
 c( triplets_negative_gi [, "oln_id_a"], triplets_negative_gi [, "oln_id_b"] ) %>% unique() %>% length()

 ###################
# Kinase-substrate network

 kinase_network_filtered_triplets_a <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "kd" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))

  kinase_network_filtered_triplets_b <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "ku" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
              							dplyr::rename( temp=oln_id_a) %>%
              							dplyr::rename( oln_id_a=oln_id_b) %>%
                            dplyr::rename( oln_id_b=temp)

  kinase_network_filtered_triplets <- dplyr::union  (kinase_network_filtered_triplets_a, kinase_network_filtered_triplets_b ) %>%
					dplyr::distinct()

 # Number of interactions
 kinase_network_filtered_triplets  %>%
     dplyr::distinct()%>%
     dplyr::count()

 # Number of proteins
 c( kinase_network_filtered_triplets [, "oln_id_a"], kinase_network_filtered_triplets [, "oln_id_b"] ) %>% unique() %>% length()

 # Number of kinases 
 kinase_network_filtered_triplets [, "oln_id_a"]  %>% unique() %>% length()

 ###################
 # Protein interaction network
  sbi_interactome_triplets_a <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "p" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))

  sbi_interactome_triplets_b <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "p" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
              							dplyr::rename( temp=oln_id_a) %>%
              							dplyr::rename( oln_id_a=oln_id_b) %>%
                            dplyr::rename( oln_id_b=temp)

  sbi_interactome_triplets <- dplyr::union  (sbi_interactome_triplets_a, sbi_interactome_triplets_b ) %>%
					                    dplyr::distinct() %>%
				                      dplyr::filter( oln_id_a > oln_id_b )

  # Number of interactions
 sbi_interactome_triplets  %>%
     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
     dplyr::filter( oln_id_a > oln_id_b) %>%
     dplyr::distinct()%>%
     dplyr::count()

  # Number of proteins
 c( sbi_interactome_triplets [, "oln_id_a"], sbi_interactome_triplets [, "oln_id_b"] ) %>% unique() %>% length()

# Transcriptional regulatory network

  tf_network_collated_triplets_a <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "td" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))

  tf_network_collated_triplets_b <- interactions_from_triplet_motifs_simp %>%
                            dplyr::filter(interaction_type_abbrev == "tu" )  %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
              							dplyr::rename( temp=oln_id_a) %>%
              							dplyr::rename( oln_id_a=oln_id_b) %>%
                            dplyr::rename( oln_id_b=temp)

  tf_network_collated_triplets <- dplyr::union  (tf_network_collated_triplets_a, tf_network_collated_triplets_b ) %>%
					dplyr::distinct()

# Number of interactions
 tf_network_collated_triplets %>%
     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
     dplyr::distinct()%>%
     dplyr::count()

# Number of proteins
 c( tf_network_collated_triplets [, "oln_id_a"], tf_network_collated_triplets [, "oln_id_b"] ) %>% unique() %>% length()

# Number of transcription factors
 tf_network_collated_triplets %>%
     dplyr::select (one_of(c("oln_id_a"))) %>%
     dplyr::distinct()%>%
     dplyr::count()

# Total Number of Interactions (Unique Pairs of Proteins)
  interactions_from_triplet_motifs_simp_a <- interactions_from_triplet_motifs_simp %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))

  interactions_from_triplet_motifs_simp_b <- interactions_from_triplet_motifs_simp %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
              							dplyr::rename( temp=oln_id_a) %>%
              							dplyr::rename( oln_id_a=oln_id_b) %>%
                            dplyr::rename( oln_id_b=temp)

  unique_interactions_from_triplet_motifs <- dplyr::union  (interactions_from_triplet_motifs_simp_a, interactions_from_triplet_motifs_simp_b ) %>%
					dplyr::distinct()  %>%
				  dplyr::filter( oln_id_a > oln_id_b )

 unique_interactions_from_triplet_motifs %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
  dplyr::distinct() %>%
  dplyr::count()

# Total Number of Proteins 
 c( unique_interactions_from_triplet_motifs [, "oln_id_a"], unique_interactions_from_triplet_motifs [, "oln_id_b"] ) %>% unique() %>% length()

# Total Number of Interactions (Non-unique pairs and direction)
 triplets_negative_gi %>% 
 dplyr::bind_rows( kinase_network_filtered_triplets ) %>%
 dplyr::bind_rows(sbi_interactome_triplets ) %>%
 dplyr::bind_rows( tf_network_collated_triplets ) %>%
  dplyr::count()
